---
name: Ivana
surname: Cardoso
position: "Phd Candidate"
address: "Graduate Program in Ecology, National Institute of Amazonian Research (INPA)"
profilepic: ivanacardoso.jpg
email: "ivanawaters@gmail.com"
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "My skills involve programming in R and LaTeX, Data Analysis and GIS software proficiency. Furthermore, I can speak, read, write and understand English and Portuguese. ORCID: 0000-0003-2662-6426."
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Summary

I am undergraduated in Biological Sciences ([Instituto Federal Farroupilha](https://www.iffarroupilha.edu.br/julio-de-castilhos) - 2019) and hold a master's degree in Ecology and Conservation ([Universidade Estadual de Santa Cruz](https://www.ecologiauesc.com/) - 2022). Currently, I am a Ph.D. candidate in Ecology at the [National Institute of Amazonian Research](http://ppginpa.eco.br/index.php/pt-br/), and my research is focused on the spatiotemporal effects of forest insularization on biodiversity. I am interested in ecology, biodiversity conservation, and ornithology.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Undergraduation in Biological Sciences", "2015-2019", "Instituto Federal Farroupilha", "Júlio de Castilhos, RS, Brazil",
  "Masters in Ecology and Conservation", "2020-2022", "Universidade Estadual de Santa Cruz", "Ilhéus, BA, Brazil",
  "PhD in Ecology", "2023-", "Instituto Nacional de Pesquisas da Amazônia", "Manaus, AM, Brazil"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Work Experience

June 2016 - present

-   In 2016, I volunteered for the Chico Mendes Institute for Biodiversity Conservation, participating in the research project [Ecological Impacts of River Damming on forest Bird Assemblages in the Brazilian Amazon](https://www.rufford.org/projects/anderson-saldanha-bueno/ecological-impacts-of-river-damming-on-forest-bird-assemblages-in-the-brazilian-amazon/). In this project, we sampled understory birds in 33 forest islands and five continuous forest using mist-nets.

-   In 2021, I conducted a project research to assess the influence of landscape and local variables on multiple facets of bird diversity in eucalypt plantations distributed in Atlantic Forest landscapes. In this project, we sampled understory birds in 19 eucalypt plantations using mist-nets.

-   In 2022, I participated in a research project to assess whether plantations of native coniferous trees (*Araucaria angustifolia*) and exotic ones (*Pinus elliottii*) are capable of sustaining forest avifauna. In this project, we surveyed 18 sample points using mist-nets.

-   In 2022, I surveyed 68 forest islands using audio recorders in the Balbina Hydroelectric Reservoir to assess the conservation status of biodiversity on forested islands of varying sizes.

# Prizes

Helmut Sick Award - 1st place for undergraduate student oral presentation at the XXVI Congresso Brasileiro de Ornitologia (2019). Awarded by [Sociedade Brasileira de Ornitologia](https://ararajuba.org.br/congressos-e-premios/premio-helmut-sick/)

# Bibliographic production

Original research published in journals:

1.  CARDOSO, I.; BUENO, A. S.; MORANTE-FILHO, J. C.[Number of forest fragments and understory plants exert opposite effects on multiple facets of bird diversity in eucalypt plantations](https://link.springer.com/article/10.1007/s10980-023-01601-5). Landscape Ecology, v.3, p.1 - 15, 2023.

Most relevant abstracts published in proceedings of events:

1.  CARDOSO, I.; AMARANTE, R. T.; AMARANTE, R. T.; FERNANDES, F. B.; BUENO, A. S. [Functional diversity of understory birds in natural forests and coniferous tree plantations in the Araucaria Moist Forests ecoregion](https://drive.google.com/file/d/1lBvOCiUP8OnjExJq9binFBtBvVQvBr7H/view) In: II Ornithological Congress of the Americas, 2023. Abstract book, page 199, 2023.

2.  CARDOSO, I.; BUENO, A. S.; PERES, C. A. [Ambientes de borda criados por insularização florestal abrigam avifaunas empobrecidas](chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/https://ararajuba.org.br/wp-content/uploads/2019/09/LIVRO-DE-RESUMOS-XXVI-CBO.pdf) In: XXVI Congresso Brasileiro de Ornitologia, 2019. Livro de resumos, page 34, 2019.

3.  CARDOSO, I.; BUENO, A. S.; PERES, C. A. [Classifying edge tolerance in understory birds in Amazonian forest islands: a quantitative approach](https://www.researchgate.net/publication/346446147_Classifying_edge_tolerance_in_understory_birds_in_Amazonian_forest_islands_a_quantitative_approach) In: Ornithological Congress of the Americas, 2017. [Book of abstracts](chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/https://afonet.org/uploads/2017_OCA_Abstracts.pdf), page 237, 2017.
